On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages

### 2020-09-24 paper/paper.tex
Started on conclusion

\subsection{Connection to Church encodings}
% \begin{todo}
%   Work on this subsection. Maybe this shouldn't be a separate section at all and
%   maybe its contents should be incorporated throughout the rest of the paper.
% \end{todo}

@@

\clearpage
\section{Related Work}

>>>>

\subsection{Connection to Church encodings}
\label{sec:Church}
% \begin{todo}
%   Work on this subsection. Maybe this shouldn't be a separate section at all and
%   maybe its contents should be incorporated throughout the rest of the paper.
% \end{todo}

@@

\section{Conclusion}

\begin{todo}
Should some of this go into the introduction?
\end{todo}

In this paper:
\begin{itemize}
  \item We address the goal of translating Haskell pattern matching into an
    EDSL. An example usage of this mechanism is given in Section
    \ref{sec:CBackend} in the form of a transformation of a subset of Haskell
    into an EDSL that is then used to generate C code, effectively compiling
    that subset of Haskell into C.

  \item A representation of pattern matching via a deep embedding of Church
    encodings of products and coproducts presented in Section \ref{sec:Church}.
    This encoding relies on having a uniform representation of algebraic data
    types.

  \item To provide the uniform representation of algebraic data types mentioned
    in the previous point, we describe a mechanism for automatically encoding
    ADTs as compositions of \verb|(,)|, \verb|Either| and \verb|()| using
    \verb|ERep| and \verb|ERepTy| in Section \ref{sec:ADTRep}.

  \item A GHC plugin is outlined in Section \ref{sec:CorePlugin} which provides automation for the translation of
    Haskell code into these EDSL representations.

\end{itemize}

\begin{todo}
Should we have a diagram somewhere in the paper to show how these pieces all fit together?
\end{todo}

\section{Related Work}
